Detecting Hand Direction for Computer Interaction

### 2014-12-13 paper/paper.tex
Paper modifications.

%%%%%%%%% ABSTRACT
\begin{abstract}
We present a method for detecting the direction of a pointing hand in an image for the purpose of creating a computer interface based on pointing.  Given an image that is dominated by a pointing hand, extract features and use regression to determine where it points.  We collected a set of images to use for comparing performance on this task.  We evaluated the performance of two different features for the regression: convolutional neural networks and histograms of oriented gradients.  We also compared two different methods of performing the regression: k-Nearest Neighbors and least squares linear regression.  This approach differs from many previous works in that it focuses on detecting the angle of a single finger in relation to the screen rather than on estimating hand poses or recognizing gestures.

@@

We collected a set of images to evaluate the relative effectiveness of different methods.  These images were collected from a standard webcam directly above a computer screen.  Each picture contained a pointing hand to recognize on a blank background.  The hand was approximately one foot away from the camera and screen.  To keep hand location consistent, the user was shown a video of their hand as they recorded and attempted to keep their hand on a crosshair overlayed at the center of the image.  A dot was displayed on the screen and the user pointed at the dot as it moved across the screen.  The dot moved along a seven by seven grid with spacing of 80 pixels and for each location, a picture was taken of the user pointing at that location from the webcam.  We repeated this grid collection procedure 15 times, collecting a total of 735 images.

@@

To test our system's effectiveness for computer interaction, we used the HOG feature based system to predict where a user was pointing at a computer screen.  We used the prediction to move a dot on the screen, which simulated the movement of a computer mouse.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
We present a method for detecting the direction of a pointing hand in an image for the purpose of creating a computer interface based on pointing.  Given an image that is dominated by a pointing hand, we extract features and use regression to determine where it points.  We collected a set of images to use for comparing performance on this task.  We evaluated the performance of two different features for the regression: convolutional neural networks and histograms of oriented gradients.  We also compared two different methods of performing the regression: k-Nearest Neighbors and least squares linear regression.  This approach differs from many previous works in that it focuses on detecting the angle of a single finger in relation to the screen rather than on estimating hand poses or recognizing gestures.

@@

We collected a set of images to evaluate the relative effectiveness of different methods.  These images were collected from a standard webcam directly above a computer screen.  Each picture contained a pointing hand on a blank background.  The hand was approximately one foot away from the camera and screen.  To keep hand location consistent, the user was shown a video of their hand as they recorded and attempted to keep their hand on a crosshair overlayed at the center of the image.  A dot was displayed on the screen and the user pointed at the dot as it moved across the screen.  The dot moved along a seven by seven grid with spacing of 80 pixels and for each location, a picture was taken of the user pointing at that location from the webcam.  We repeated this grid collection procedure 15 times, collecting a total of 735 images.

@@

To test our system's effectiveness for computer interaction, we used the system based on HOG features to predict where a user was pointing on a computer screen.  We used the prediction to move a dot on the screen, which simulated the movement of a computer mouse.
